\Title

### 2020-03-03 manuscript/manuscript.tex
Add nb for creating source layouts schematic figure

@@

\begin{figure*}
    \includegraphics[width=\linewidth]{figs/ground_survey_differences.pdf}
    \caption{
        Differences between gravitational effects measured on the target grid
        and the ones produced by the best prediction made by each source
        distribution based on the synthetic ground survey.
    }
    \label{fig:ground-survey-differences}
\end{figure*}

\begin{figure*}
    \includegraphics[width=\linewidth]{figs/airborne_survey_differences.pdf}
    \caption{
        Differences between gravitational effects measured on the target grid
        and the ones produced by the best prediction made by each source
        distribution based on the synthetic airborne survey.
    }
    \label{fig:airborne-survey-differences}
\end{figure*}

>>>>

\begin{figure*}
    \includegraphics[width=\linewidth]{figs/source-layouts-schematics.pdf}
    \caption{
        Source layouts.
        (a) Set of synthetic observation points that resemble a ground survey.
        (b) Location of sources obtained through the \emph{sources beneath
            data} layout.
        (c) Location of sources obtained through the \emph{block averaged
            sources} layout.
        (d) Location of sources obtained through the \emph{grid sources}
            layout.
    }
    \label{fig:source-layouts-schematics}
\end{figure*}

@@
